### 2024-12-02 README.Rmd
badges

<!-- badges: start -->
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/rimonim/embedplyr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rimonim/embedplyr/actions/workflows/R-CMD-check.yaml)
[![codecov test coverage](https://codecov.io/github/rimonim/embedplyr/graph/badge.svg?token=CNJZ8R2LYZ)](https://codecov.io/github/rimonim/embedplyr)
<!-- badges: end -->
